A Geometry for Network Visualization in \MakeLowercase{\texttt{ggplot2}}

### 2015-03-30 CC/writeup.Rnw
email example facetting

\sct{This network is plotted in figure \ref{fig.cap:email_ex}.  This plot is very crowded, and it is difficult to distinguish structure in the network when it there is so much over-plotting.  To remedy this, we facet the network by day to examine how the company's communications change throughout the week. }
<<email_ex_facet, fig.height=8, fig.width=8, fig.cap = 'All emails within a company over a two week period facetted by day of the month.'>>=
ggplot(data = email.net, aes(from_id = From, to_id = to, )) +
  geom_net(vertices = email.names,ealpha = 0.1, vsize = I(2), directed = TRUE) +
  expand_limits(x=c(0,1), y = c(0,1)) +
  facet_wrap(~day, nrow = 2) +
  theme_net #add direction later
@
\begin{landscape}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figure/email_ex_facet-1.pdf}
\caption{\label{fig.cap:email_ex_facet} The same email network as in figure \ref{fig.cap:email_ex} facetted by day of the week.}
\end{figure}
\end{landscape}

>>>>

\sct{This network is plotted in figure \ref{fig.cap:email_ex}.  This plot is very crowded, and it is difficult to distinguish structure in the network when it there is so much over-plotting.  To remedy this, we facet the network by day to examine how the company's communications change throughout the week. }
<<email_ex_facet, fig.height=8, fig.width=8, fig.cap = 'All emails within a company over a two week period facetted by day of the month.'>>=
ggplot(data = subset(email.net, nrecipients < 54), aes(from_id = From, to_id = to, )) +
  geom_net(vertices = employee,ealpha = 0.1, vsize = I(2), directed = TRUE,
           aes(vcolour=cols[as.numeric(CurrentEmploymentType)])) +
  expand_limits(x=c(0,1), y = c(0,1)) +
  facet_wrap(~day, nrow = 2) +
  theme_net
@
\begin{landscape}
\begin{figure}
\centering
\includegraphics[width=\textwidth]{figure/email_ex_facet-1.pdf}
\caption{\label{fig.cap:email_ex_facet} The same email network as in figure \ref{fig.cap:email_ex} facetted by day of the week.}
\end{figure}
\end{landscape}
